Verifying Demonstrations

### 2018-11-22 paper/adversary-model.tex
Changes adversary definitions to A{1,2,3} form

\begin{definition}[Base adversary]%
  \label{base-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
  communication occurred \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly from the communication medium, only if those appear in the data 
    \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{definition}

@@

\begin{definition}[Deanonymizing-witness adversary]%
  \label{deanonymizing-witness-adversary}
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{definition}

@@

\begin{definition}[Deanonymizing adversary]%
  \label{deanonymizing-adversary}
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{definition}

>>>>

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The protester \(P\) and the witness \(W\) communicate.
  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
  communication occurred \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly from the communication medium, only if those appear in the data 
    \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{adversaries}

@@

\begin{adversaries}
\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{adversaries}

@@

\begin{adversaries}
\item\label{deanonymizing-adversary}
  \emph{Fully deanonymizing adversary}:
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}
